PANCHANGE_analysis

### 2020-08-20 PANCHANGE_analysis.Rmd
hierarchy

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("eeptools")
#install.packages("skimr")
```

Install packages
```{r}
#install.packages("infer")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(infer)
library(patchwork)
library(broom)
library(tidyverse)
```

@@

>>>>

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("broom")
#install.packages("skimr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(patchwork)
library(broom)
library(tidyverse)
```

@@

# Psychiatric disorder hierarchy
```{r}
dat %>%
  mutate(
    Disorder_exclusive_numeric =
      case_when(
        control_numeric == 1 ~ 0 
        depressive_disorders_numeric = "Depressive disorders",
        anxiety_disorders_numeric = "Anxiety disorders",
        mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
        eating_disorders_numeric = "Eating disorders",
        obsessive_compulsive_disorders_numeric = "OCDs",
        mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
        mhd.personality_disorder_numeric == 1 ~ 7,
        mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
        psychotic_disorders_numeric == 1 ~ 10,
           ))

      )
  )

dat %>%
  mutate(
    Disorder_exclusive =
      recode_factor(
        Disorder_exclusive,
        "0" = "Controls",
        "4" = 
        "5" = "OCDs"
        "6" = "ADHD"
        "7" = "Personality disorders"
        "8" = "Autism",
        "9" = "Bipolar disorders",
        "10" = "Psychotic disorders"
      )
  )
